The Holy Hand Grenade of Antioch

### 2020-02-23 draft-camelot-holy-grenade.tex
feat: bumpt to tex2mn 0.4.1 usage

@@

\begin{note}
  \mn{display=true,source=Author}
  Image courtesy of
  % TODO \href apparently not working
  {https://camelot.gov.example/creatures-in-ascii/}
\end{note}

@@

\begin{figure}[h]\centering
  \mn{foo}
  \label{sovereign-orb}
  \caption{The Sovereign's Orb made invisible}
  % TODO: \mn{link=https://upload.wikimedia.org/wikipedia/commons/b/bf/Coa_Illustration_Elements_Globus_cruciger.svg,align=right}
  % TODO: image::https://camelot.gov.example/sovereigns_orb.jpg[Orb,124,135]
  %       \includegraphics[width=135,height=124]{https://camelot.gov.example/sovereigns_orb.jpg}
  \includegraphics[width=\textwidth]{example-image-a}
\end{figure}

@@

% TODO: what are (((...))) ?
The solution to the impasse at the ((Cave of Caerbannog)) was
provided by the successful deployment of the
\textbf{Holy Hand Grenade of Antioch} (see \mncite{hand-grenade-figure})
(((Holy Hand Grenade of Antioch))).
Any similarity between the Holy Hand Grenade of Antioch and the
mythical \textit{Holy Spear of Antioch} is purely intentional;
(((relics, Christian))) any similarity between the Holy Hand Grenade
of Antioch and the \textit{Sovereign's Orb of the United Kingdom}
(see \mncite{sovereign-orb}) is putatively fortuitous.
(((relics, monarchic)))

>>>>

\usepackage[T1]{fontenc}
\usepackage{textcomp}

@@

\begin{note}
  \mn{display=true,source=Author}
  Image courtesy of \url{https://camelot.gov.example/creatures-in-ascii/}
\end{note}

@@

\begin{figure}[h]\centering
  \mn{link=https://upload.wikimedia.org/wikipedia/commons/b/bf/Coa_Illustration_Elements_Globus_cruciger.svg,align=right}
  \label{sovereign-orb}
  \caption{The Sovereign's Orb made invisible}
  % TODO: image::https://camelot.gov.example/sovereigns_orb.jpg[Orb,124,135]
  %       \includegraphics[width=135,height=124]{https://camelot.gov.example/sovereigns_orb.jpg}
  \includegraphics[width=\textwidth]{example-image-a}
\end{figure}

@@

% TODO: implement indexing, i.e. (((...)))
The solution to the impasse at the ((Cave of Caerbannog)) was
provided by the successful deployment of the
\textbf{Holy Hand Grenade of Antioch} (see \mncite{hand-grenade-figure})
(((Holy Hand Grenade of Antioch))).
Any similarity between the Holy Hand Grenade of Antioch and the
mythical \textit{Holy Spear of Antioch} is purely intentional;
(((relics, Christian))) any similarity between the Holy Hand Grenade
of Antioch and the \textit{Sovereign's Orb of the United Kingdom}
(see \mncite{sovereign-orb}) is putatively fortuitous.
(((relics, monarchic)))
